---
title: "Group-project-code"
format: html
---

```{r}

# Option 2: Read directly from GitHub
groundhogs <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2024/2024-01-30/groundhogs.csv')
predictions <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2024/2024-01-30/predictions.csv')

```

```{r}
library(tidyverse)
library(viridis)

groundhogs <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/main/data/2024/2024-01-30/groundhogs.csv')
predictions <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/main/data/2024/2024-01-30/predictions.csv')

groundhogs_all <- predictions |> 
   left_join(groundhogs, join_by(id==id)) |> 
  filter(region == "Pennsylvania")
```

```{r}
# Read Weather Data 
library(readr)
Actual_weather <- read_csv("../../data/data.csv", skip = 3)
```

```{r}
Actual_weather <- Actual_weather |> 
  mutate(year = as.numeric (str_sub(Date, 1,4)))
```

```{r}
groundhogs_final <- groundhogs_all|> 
  left_join(Actual_weather, join_by(year == year))
```

```{r}
groundhogs_final <- groundhogs_final %>%
  mutate(earlyspring = Value >= 37) |> 
  mutate(accuracy = shadow != earlyspring) |>
  mutate(type = str_replace(type, "Taxidermied groundhogs", "Taxidermied groundhog")) |> 
  filter(!is.na(accuracy))
```

```{r}
ggplot(groundhogs_final, aes(x = accuracy, fill = type)) +
  geom_bar()+
  scale_fill_manual("Type of Groundhog", values = viridis(5)) +
  labs(x = "Groundhog Accuracy", y = "Count Predictions", title = "Accuracy of Groundhog Predictions", caption = "Data from groundhog-day.com and NOAR", alt = "Bar Graph of ground hog prediction acuracy by type of goundhog. Groundhogs are more accurate than not, but not by much") +
  theme_bw()

ggplot(groundhogs_final, aes(x = accuracy, fill = type)) +
  geom_bar()+
  facet_wrap(~earlyspring, labeller = as_labeller(c(
    `TRUE` = "Early Spring",
    `FALSE` = "Winter"
  ))) +
  scale_fill_manual("Type of Groundhog", values = viridis(5)) +
  labs(x = "Groundhog Accuracy", y = "Count Predictions", title = "Accuracy of Groundhog Predictions", caption = "Data from groundhog-day.com and NOAR", alt = "Bar Graph of ground hog prediction acuracy by type of goundhog. Groundhogs are more accurate than not, but not by much") +
  theme_bw()


ggplot(groundhogs_final, aes(y = type, fill = accuracy)) +
  geom_bar(position = "fill", color = "white")+
  scale_fill_manual("Groundhog Accuracy", values = viridis(2)) +
  labs(x = "Percent of Predictions", y = "Type of Groundhog", title = "Proportion of Acurate Groundhog Predictions by Type", caption = "Data from groundhog-day.com and NOAR") +
  theme_bw()

ggplot(groundhogs_final, aes(x = year, y = Value, color = accuracy)) +
  geom_point() +
  scale_color_manual("Groundhog Accuracy", values = viridis(2)) +
  labs(x = "Year of Prediction", y = "Average Temperature", title = "Prediction Acuracy by Temperature Over Time", caption = "Data from groundhog-day.com and NOAR") +
  geom_hline(yintercept = 37, color = "red", linetype = "dashed") +
  theme_bw()
```

# Map of Groundhogs in Pennsylvania

```{r}
library(mosaic)

#Tribble dataset

groundhog_location <- tribble(
  ~name, ~longitude, ~latitude, ~type,
  "Punxsutawney Phil",-78.96225, 40.9312, "Groundhog", 
  "Octoraro Orphie", -76.09196, 39.82554, "Taxidermied groundhog",
  "Schnogadahl Sammi",-75.49787, 40.90142, "Taxidermied groundhog",
  "Poor Richard", -76.72926, 39.96586, "Taxidermied groundhog",
  "Uni the Groundhog", -76.29992, 40.41813, "Taxidermied groundhog",
  "Grover and Sue", -76.36766, 40.57162, "Taxidermied groundhog",
  "Dover Doug", -76.85717, 39.99791, "Person in a groundhog suit",
  "Lawrenceville Lucy", -77.20171, 41.97356, "Groundhog",
  "Mount Joy Minnie", -76.50431, 40.10912, "Plush groundhog",
  "Patty Pagoda", -75.90783, 40.33607, "Person in a groundhog suit",
  "Tinicum Tim", -75.25721, 39.89215, "Groundhog puppet",
  "Harleysville Hank", -75.38234, 40.29050, "Plush groundhog",
  "Mount Gretna Grady", -76.46776, 40.24677, "Plush groundhog",
  "Poppy the Groundhog", -76.66445, 40.12133, "Groundhog",
  "MT Parker", -76.30730, 40.05880,	"Plush groundhog"
)
```

```

```{r}
library(gplots)
library(leaflet)
library(htmlwidgets)


#Map
groundhog_map <- leaflet(data = groundhog_location) |>
  addTiles() |>
  addCircles(color = ~colorFactor(c("darkred","darkgreen","red","darkblue","orange"), domain= groundhog_location$type)(type), label = groundhog_location$name) |>
   addLegend(position = "bottomright",
            colors = c("darkred","darkgreen","red","darkblue","orange"), labels = c("Groundhog","Groundhog Puppet", "Person in a groundhog suit", "Plush groundhog","Taxidermied groundhog"), title ="Type")

saveWidget(groundhog_map, file = "groundhog_map.html")

```

```{r}
#filtered data

groundhogs_penn <- groundhogs_all |> 
  filter(region == "Pennsylvania")

```

